Comprehensive Quality-Aware Automated Semantic Web Service Composition

### 2017-05-12 paper.tex
format

To analyse the effectiveness of achieving a good comprehensive quality at the expense of slightly reduced QoS, we demonstrate two best solutions produced using Task 3 as an example. Fig. \ref{comparisontest} $(1)$ and $(2)$ show two weighted DAGs $WG_1$ and $WG_2$ that have been obtained as the best service compositions solutions based on the QoS model and on the comprehensive quality model, respectively. Both $WGs$ have exactly the same service workflow structure, but some service vertices and edges denoted in red are different. To better understand these differences, we list the overall semantic matchmaking quality $SM$,  overall $QoS$ and semantic matchmaking quality $sm_{e_n}$ associated to these different edges in $WG_1$ and $WG_2$. (Note: $sm_{e_n} = 0.5type_{e_n} + 0.5 sim_{e_n}$), where $\Delta Q$ reveals the gain (positive $\Delta Q$) or a loss (negative $\Delta Q$) of the listed qualities for our comprehensive quality model. Therefore, we achieve a comprehensive quality gain of 0.1433, which is the result of a gain in semantic matchmaking quality (+0.1467) and a loss in $QoS$ (-0.0034). To understand the improvement of semantic matchmaking quality from these numbers, we pick up $e_4$ that is associated with the smallest $\Delta Q$. The $e_4$ of $WG_1$ and $WG_2$ has two different source nodes, $Ser1640238160$ and $Ser947554374$, and two the same end nodes. $Ser1640238160$ and $Ser947554374$ are services with output parameters $Inst582785907$ and  $Inst795998200$ corresponds to two concepts $Con2037585750$ and $Con103314376$ respectively in the given ontology shown in Fig. \ref{comparisontest} $(4)$. As $Inst658772240$ is a required parameter of $End$, and related to concept $Con2113572083$, $Inst795998200$ is closer to the required output $Inst658772240$ than $Inst582785907$. Therefore,  $Ser947554374$ is selected with a better semantic matchmaking quality compared to $Ser1640238160$.

>>>>

To analyse the effectiveness of achieving a good comprehensive quality at the expense of slightly reduced QoS, we demonstrate two best solutions produced using Task 3 as an example. Fig. \ref{comparisontest} $(1)$ and $(2)$ show two weighted DAGs $WG_1$ and $WG_2$ that have been obtained as the best service compositions solutions based on the QoS model and on the comprehensive quality model, respectively. Both $WGs$ have exactly the same service workflow structure, but some service vertices and edges denoted in red are different. To better understand these differences, we list the overall semantic matchmaking quality $SM$,  overall $QoS$ and semantic matchmaking quality $sm_{e_n}$ associated to these different edges in $WG_1$ and $WG_2$. (Note: $sm_{e_n} = 0.5type_{e_n} + 0.5 sim_{e_n}$), where $\Delta Q$ reveals the gain (positive $\Delta Q$) or a loss (negative $\Delta Q$) of the listed qualities for our comprehensive quality model. Therefore, we achieve a comprehensive quality gain (+0.1433), a result of a gain in semantic matchmaking quality (+0.1467) and a loss in $QoS$ (-0.0034). To understand the improvement of semantic matchmaking quality from these numbers, we pick up $e_4$ that is associated with the smallest $\Delta Q$. The $e_4$ of $WG_1$ and $WG_2$ has two different source nodes, $Ser1640238160$ and $Ser947554374$, and two the same end nodes. $Ser1640238160$ and $Ser947554374$ are services with output parameters $Inst582785907$ and  $Inst795998200$ corresponds to two concepts $Con2037585750$ and $Con103314376$ respectively in the given ontology shown in Fig. \ref{comparisontest} $(4)$. As $Inst658772240$ is a required parameter of $End$, and related to concept $Con2113572083$, $Inst795998200$ is closer to the required output $Inst658772240$ than $Inst582785907$. Therefore,  $Ser947554374$ is selected with a better semantic matchmaking quality compared to $Ser1640238160$.
